README.md

### 2021-10-14 README.Rmd
AoB 1st revision 🔎

# Seed germination ecology of European mesic grasslands

This repository stores all the information related to the manuscript *Seed germination ecology of European mesic grasslands*, including the raw datasets, the scripts to perform data cleaning and analysis, and the `Rmarkdown` files to create the manuscript.

@@

* `data` Data files including the seed germination dataset, the species traits, and the phylogenetic tree.
* `doc` Files to create the manuscript using `Rmarkdown`.
* `results` Output of the `R` scripts, including figures and models.
* `src` Scripts in `R` language used to clean the raw data and perform the analyses of the manuscript.

>>>>

# Seed ecology of European mesic meadows

This repository stores all the information related to the manuscript *Seed ecology of European mesic meadows*, including the raw datasets, the scripts to perform data cleaning and analysis, and the `Rmarkdown` files to create the manuscript.

@@

* `data` Data files including the seed trait datasets (European, Iberian and Cantabrian) and the phylogenetic tree.
* `doc` Files to create the manuscript using `Rmarkdown`.
* `results` Output of the `R` scripts, including figures and models.
* `src` Scripts in `R` language used to clean the raw data and perform the analyses of the manuscript.
